Open Linked Social Data for Scientific Benchmarking

### 2016-06-30 paper.tex
minor changes

\section{Introduction}
The enormity of the digital data makes a rapid development of various methods of data analysis,
giving an opportunity to analyze the data from a different perspectives.

@@

\section{Materials: data from diverse provenance}

\section{Methods: linked open data}
\subsection{RDF}
\subsection{Data-driven ontology synthesis}

>>>>

\section{Introduction}
The enormity of the digital data propels a rapid development of data analysis methods,
implying analyzes from different perspectives.

@@

\section{Materials: data from diverse provenance}\label{materials}

\section{Methods}

\subsection{Linked open data}
\subsection{RDF}
\subsection{Data-driven ontology synthesis}
